Tight Bounds for Online Balanced Graph Partitioning

### 2020-05-08 paper/disc20clustering.tex
Comments back
Comments
wip

 %\newcommand\mahmoud[1]{\color{orange}\textbf{Mahmoud: #1~}\color{black}}
 \newcommand\stefan[1]{\color{blue}\textbf{Stefan: #1}\color{black}}
 %\newcommand\maciek[1]{\color{brown}\textbf{(Maciek: #1)}\color{black}}
 \newcommand\mahmoud[1]{}
 %\newcommand\stefan[1]{}
 \newcommand\maciek[1]{}

@@

@@

\begin{table*}
	\centering
	\renewcommand{\arraystretch}{1.5}
	\begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
		\rowcolor{gray!50}
		\textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
		\textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 6\hspace{0.3cm}(\S \ref{sec:k2}) \\ 
		\rowcolor{gray!25}
		\textbf{$k=3$}&  $\Omega(\ell)$ \hspace{0.3cm}(\S \ref{sec:lowerbound})& $O(\ell) $\hspace{0.3cm}(\S \ref{sec:k3})\\
		$k > 3$ & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k^2 \cdot \ell^2)$\hspace{0.1cm} \cite{repartition-disc} \\
		\rowcolor{gray!25}
		Learning model & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k \cdot \ell)$\hspace{0.3cm} (\S \ref{sec:ppl}) \\
	\end{tabular}
	\caption{Overview of known results and the results provided in this paper. By $\Rep$ we denote the cost of a single component repartition, and we elaborate on this in Section~\ref{sec:k3}. The results pertain to the general partitioning model, but the last row, that pertains to the learning model for arbitrary $k$ and $\ell$.
	}
	\label{tab:overview}
	\vspace{-7mm}
\end{table*}

@@

We provide a lower bound $\Omega(k\cdot \ell)$ for the competitive ratio of any deterministic online algorithm for the learning problem.
Later we elaborate on how to efficiently transform it to a lower bound for the partitioning problem.
The lower bound requires $k\geq 3$.
For $k=2$, the learning problem is trivial: immediate collocation of a communicating pair is $1$-competitive.
(A partitioning problem for $k=2$ is non-trivial, a lower bound of $3$ is known \cite{repartition-disc}, and we provide a $6$-competitive algorithm (see Section~\ref{sec:k2}).)

@@

\begin{lemma}
	\label{lem:1req}
	During a single reconfiguration of nodes, \TAlg exchanges at most $2$ pairs of nodes.
\end{lemma}

>>>>

 \newcommand\mahmoud[1]{\color{orange}\textbf{Mahmoud: #1~}\color{black}}
 \newcommand\stefan[1]{\color{blue}\textbf{Stefan: #1}\color{black}}
 \newcommand\maciek[1]{\color{brown}\textbf{(Maciek: #1)}\color{black}}
 %\newcommand\mahmoud[1]{}
 %\newcommand\stefan[1]{}
 %\newcommand\maciek[1]{}

@@

\maciek{TODO style: documentclass[a4paper,anonymous,USenglish] lipics-v2019.}
\maciek{Keywords: distributed computing?}

@@

\begin{table*}
	\centering
	\renewcommand{\arraystretch}{1.5}
	\begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
		\rowcolor{gray!50}
		\textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
		\textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 6\hspace{0.3cm}(\S \ref{sec:k2}) \\ 
		\rowcolor{gray!25}
		\textbf{$k=3$}&  $\Omega(\ell)$ \hspace{0.3cm}(\S \ref{sec:lowerbound})& $O(\ell) $\hspace{0.3cm}(\S \ref{sec:k3})\\
		$k > 3$ & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k^2 \cdot \ell^2)$\hspace{0.1cm} \cite{repartition-disc} \\
		\rowcolor{gray!25}
		Learning model & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k \cdot \ell)$\hspace{0.3cm} (\S \ref{sec:ppl}) \\
	\end{tabular}
	\caption{Overview of known results and the results provided in this paper. By $\Rep$ we denote the cost of a single component repartition, and we elaborate on this in Section~\ref{sec:k3}. The first three rows show the results for the general partitioning model, and last row shows the results for the learning model for arbitrary $k$ and $\ell$.
	}
	\label{tab:overview}
	\vspace{-7mm}
\end{table*}

@@

We provide a lower bound $\Omega(k\cdot \ell)$ for the competitive ratio of any deterministic online algorithm for the learning problem.
Later we elaborate on how to efficiently transform it to a lower bound for the partitioning problem.
The lower bound requires $k\geq 3$.
For $k=2$, the learning problem is trivial: immediate collocation of a communicating pair is $1$-competitive.
(A partitioning problem for $k=2$ is non-trivial, a lower bound of $3$ is known \cite{repartition-disc}, and we provide a~$6$-competitive algorithm (see Section~\ref{sec:k2}).)

@@

\begin{lemma}
	\label{lem:1req}
	In a single reconfiguration of nodes (after a merge of components), \TAlg exchanges at most $2$ pairs of nodes.
\end{lemma}
